A Search for Supernova Remnants in NGC\,6946

### 2018-10-04 ms.tex
Small test
Initial figures added

This is a citation to \cite{long14}0

@@

>>>>

This is a citation to \cite{long14}   OK here is a small change:

@@

\begin{figure}
\plotone{fig_s2_ha_ratio_distance.pdf}
\caption{The [S II]:\ha\ ratio for SNR candidates as a function of galactocentric radius.  Objects with ratios greater than 0.4 (the dashed line) are spectroscopically confirmed. \label{fig_s2_ha}}

\end{figure}

\begin{figure}
\plotone{fig_s2_ratio.pdf}
\caption{The [S II]6717:[S II]6731 line ratio for SNR candidates as a function of galactocentric distance.  Most candidates are near the low density limit and there is no trend with galactocentric distance.  \label{fig_s2_ratio}}
\end{figure}

\begin{figure}
\plotone{fig_reddening_gc.pdf}
\caption{Observed \hb:\ha line ratios for SNR candidates as a function of galactocentric distance. The dashed lines indicate the expected values of the line ration for E(B-V) of 0.0, 0.1, 0.3 and 1.0.  Objects near the galactic center tend to be more highly reddened than those far from the center. \label{fig_reddening}}
\end{figure}

\begin{figure}
\plottwo{fig_model_n2o3.pdf}{fig_model_s2n2.pdf}
\caption{Left: Model [O III] 5007:H$\beta$ ratio as function of the [N II] 6583:H$\alpha$ line ratio for SNRs and SNR candidates with spectra. As discussed in the text, the black, green and blue meshes correspond to shock models with a range of shock velocities and pre-shock magnetic fields, and with metallicities corresponding to the SMC, LMC, and Milky Way, respectively.  Right: Model [N II] 6583:H$\alpha$ line ratio as a function of  the [S II]:H$\alpha$ ratio. \label{fig_model}}
\end{figure}
